\documentclass[margin,line]{res}

\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[usenames,dvipsnames]{color}
%\usepackage{lastpage}
%\usepackage[lastpage,user]{zref}
\usepackage[page]{totalcount}

\usepackage{totpages}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0}
\renewcommand{\footrulewidth}{0}
\fancyfoot{}
\fancyfoot[L]{\emph {Last updated \today}}
\fancyfoot[R]{\thepage ~of 5}

\usepackage{lipsum}

\newcommand\textline[4][t]{%
  \par\smallskip\noindent\parbox[#1]{.17\textwidth}{\raggedright#2}%
 \parbox[#1]{.7\textwidth}{\raggedright#3}% 
 \parbox[#1]{.13\textwidth}{\raggedleft#4}\par\smallskip%
}

\usepackage{marvosym} % For cool symbols.

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\hypersetup{ 
colorlinks,% 
citecolor=blue,% 
filecolor=blue,% 
linkcolor=blue,% 
urlcolor=blue 
} 

\begin{document}

{\name{\textcolor{Maroon}{\LARGE	Aaron S. Erlich} \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{3in}}
Department of Political Science        &    {\it Voice:} +1 (514)-398-4756 \\            
McGill University   &    {\it E-mail:} \texttt{aaron.erlich@mcgill.ca}\\         
855 Sherbrooke Street West   &        {\it web:} \url{www.aaronerlich.com}\\
Montréal, QC, H3A 2T7  &        {\it Office:}  McTavish 24-3\\
  Canada & 
\end{tabular}

\section{\sc Academic Appointments}
{\bf McGill University}, Department of Political Science, Montréal, QC \\
\vspace*{-.1in}
\begin{list1}
\item[] Assistant Professor, {August 2016-}
\item[] Founding Member, Centre for Social and Cultural Data Science (CSCDS) , {September 2016-
\item[] Member, Centre for the Study of Democratic Citizenship (CSDC), {February 2017-

\end{list1}


\section{\sc Education}
{\bf University of Washington}, Seattle, WA\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D., Political Science, 2016
\item[] Political Methodology Certificate: Center for Statistics and the Social Sciences, 2012
\item[] M.A., Political Science, 2012
\end{list1}


{\bf Georgetown University, School of Foreign Service}, Washington, DC \\
\vspace*{-.1in}
\begin{list1}
\item[] M.A., European Studies, \emph{with distinction},  2006
  \begin{list2}
\item[] Certificate in Refugee and Humanitarian Emergencies

\end{list2}
\end{list1}

{\bf Dartmouth College}, Hanover, NH\\
%{\em Department of XXX and XXX} 
\vspace*{-.1in}
\begin{list1}
\item[] B.A., \emph{cum laude}, Government,  2002
\end{list1}

\section{\sc Research Interests}
\textbf{Substantive}: Political economy of development, public opinion
and voting behavior, political participation in new
democracies, election fraud and
political corruption, democratization,  labor migration, post-Soviet states, Sub-Saharan Africa.

\textbf{Methodological}: Randomized impact evaluation,
lab-in-the-field experiments, survey design and analysis, development engineering, big data, ethnography, elite
interviews, mixed-methods designs.

\section{\sc Peer-Reviewed Publications}
 ``‘The local
  \emph{mwananchi} has lost trust’: Design, transition, and legitimacy
  in Kenyan election management.' 2016. \emph{Journal of Modern African
    Studies} 54(4): 671-702. (with Nicholas Kerr)

``Power of the Panopticon? How Leaders' Images Affect
Compliance.'' 2016.
\emph{Comparative Political Studies} 49(13): 1704-1738. (with Sarah Bush, Lauren Prather, and Yael
Zeira)

``Competing for
Transparency: Political Competition and Institutional Reform in
Mexican States'' 2015. \emph{American Political Science Review}
109(1): 110-128. (with Daniel Berliner)

``Aligning Rights and
Interests'' 2012. \emph{World
  Development Report: Jobs Background Paper}. Washington, D.C.: World
Bank. (with Christoper Adolph, Daniel Berliner, Anne
Greenleaf, Milli Lake, Margaret Levi, and Jennifer Noveck)

\section{\sc  Other Publications}

``Development Traps and Escaping Development
Traps: What Can We Learn from Freedom of Information Laws?'' 2016. \emph{The International Trade Journal }30(5): 378-382.

``Implausible Incarceration
Data Need to Be Addressed'' 2013. \emph{The Lancet Global Health} 1(6):
e334-- e335. (with Hans Gutbrod)

``Opinion Survey Opportunities and Exit Poll
Limitations'' 2009. In \emph{Georgia -- Presidential and Parliamentary
  Elections 2008: Lessons Learned}, ed. Igor D. Gaon. Tbilisi: Council
of Europe/OSCE, pp 256--291. (with Hans Gutbrod)

``Tajikistan: from refugee sender to labor exporter.''
2006. \emph{Migration Information Source}.
 
\section{\sc Book Reviews}
``Book Review: I Say to You: Ethnic Politics and the Kalenjin in
Kenya'' 2012. \emph{Comparative Political Studies} 45(12): 1691--1695.

\section{\sc Under Review}
``The Double-edged Sword of Mobilizing Citizens via Mobile Phone in
Developing Countries'' (with Danielle Jung, James Long, and Craig
McIntosh)

``Can Information Campaigns Impact Vote-buying Preference? Evidence
From Kenya.'' 

``Differential Item Function in Sub-National Survey Data? Evidence
from Ukraine'' (with Calvin Garner)

\section{\sc Working Papers}

``Shaping Expectations with Pre-Election Information:
Evidence from a Laboratory Experiment in the Country of Georgia.''

``How Do Public Opinion Polls Impact Elite Behavior? New Theory, New
Data Collection Design.''

``Priming Gender in A Corrupt Environment: Evidence from Ukraine''

``Covering the campaign: Political Attention in the 2014 South African
Presidential Election'' (with Jeffery Arnold, Danielle Jung, and James Long)

\\
\centerline{\emph{Working paper manuscripts available on request}}


\section{\sc Manuscripts in Preparation}
``Using Big Data to Measure Government Responsiveness'' (with Benjamin
Bagozzi, Daniel Berliner and Brian Palmer-Rubin)

``Machine Learning Kenyan Elections''

``Determinants of Municipal Compliance with Freedom of Information
Requests: Evidence from Georgia. '' (with Daniel Berliner)


\section{\sc Awards} 
\textline[t]{2017}{``What's in a Tally.'' SSHRC Internal Grant}{\$5,000}
\textline[t]{2015}{``Power of the Panopticon.'' \emph{Comparative
    Political Studies: Transparency Special Issue} (with
  S.Bush, L. Prather, Y. Zeira)}{\$11,000}
\textline[t]{2015}{``Power of the Panopticon.'' Program on Middle East Political Science (with
  L. Prather)} {\$3,000}
\textline[t]{2015}{Center for Statistics \& Social Sciences Travel
  Grant } {\$1,000}
\textline[t]{2015} {Levi-Kaplan Comparative Political Economy Research
  Award} {\$2,000}
\textline[t]{2014-2015} {Chester A. Fritz Fellowship} {\$6,400}
\textline[t]{2014}{International Research \& Exchanges
  Board (IREX)} {\$9,000}
\textline[t]{2013} {Full scholarship from NYU to attend  Inaugural
  Winter Experimental Social Sciences Institute at New York University
  Abu Dhabi} {}
\textline[t]{2013} {EITM Scholarship to attend ICPSR} {}
\textline[t]{2013}{Durden Family Fellowship, University of Washington, Department of
Political Science}{\$2,300}
\textline[t]{2007}{U.S. Fulbright Program, Georgia Recipient
  (declined)}{}
\textline[t]{2004--2006}{Merit-based tuition scholarship, Georgetown
  University}{}

\section{\sc Data Sets}
``Georgian Candidates: A Relational Database of All Georgian
Candidates who Ran for National Office since Independence.'' (with
David Sichinava)

\section{\sc Professional Evaluations and Reports}

 ``Workplace Regulation, Labor Rights and Outcomes'' (with Margaret Levi, Dan Berliner, Jennifer Noveck). Report submitted to World Bank,  2012. 

``Final Evaluation of OSI's Central Eurasia Project's Labor Migration
Program.'' OSI: New York, January 2011. 

\emph{Challenges Facing Effective Governance in Georgia} (Co-edited with Mzia Mikeladze). USAID sponsored edited volume, 2010.  

``Voices of Migrants
from Georgia''  (with Kristina Vacharadze and Giorgi Babunashvili).
Danish Refugee Council: Tbilisi Georgia, February 2009.

``Labor Migration in Armenia:
A Sociological Survey of Six Communities'' (with Anush Dulgaryan and
Andrew Golda).  USAID: Yerevan, Armenia, 2009.


\section{\sc Teaching}
{\em Instructor}\\
\vspace{-.1in}
\begin{list1}

\item[] Undergraduate courses:
   \begin{list2}
   \item[] Introduction to Quantitative Social Science [POLI 311]
     (McGill)
   \item[] The Politics of Information and Transparency in the
     Developing World [POLI 422] (McGill)
\end{list2}

 \item[] Graduate courses taught:
   \begin{list2}
   \item[] Introduction to R  [CS\&SS 508] (UW)
   \item[] Quantitative Research [POLI 618] (McGill)
\end{list2}
\end{list1}

{\em Graduate Student Instructor } \\
\vspace{-.1in}
\begin{list1}
 \item[] Undergraduate courses:
   \begin{list2}
   \item[] Introduction to Comparative Politics ($\times$3) (UW)
   [POL S 204]
   \item[] Case-Based Social Statistics [STAT 321] (UW)
   \item[]Religion and World Politics [POL S 307] (UW)
     \item[] American Politics [POL S 202] (UW)
\end{list2}
\item[] Graduate courses:
   \begin{list2}
     \item [] Advances in Content Analysis Methods [POL S 559] (UW)
     \item [] Maximum Likelihood Estimation ($\times$2) [CS\&SS/POL S
       510] (UW)
\end{list2}
\end{list1}

\section{\sc Relevant Professional Experience}
{\bf National Democratic Institute of International Affairs (NDI)},
Nairobi, Kenya \& Kyiv, Ukraine

\vspace{-.3cm}
{\em Consultant} \hfill {\bf
  September 2010--}\\
\begin{list1}
\item[]-- Provided strategic design and implementation consultancy
  for over one million dollars of applied
political public opinion and focus group work.
\end{list1}

{\bf National Democratic Institute of International Affairs (NDI)}, Nairobi, Kenya
\vspace{-.3cm}

{\em Senior Program Officer, Research and Data Analysis} \hfill {\bf
  February 2010--September 2010}\\
\vspace{-.3cm}
\begin{list1} 
\item[]-- Ran NDI's  USAID program to implement the first polling station level
digitalized maps in Africa.
\item[]-- Initiated and oversaw NDI's
Norwegian-funded qualitative and quantitative research program to
investigate citizens' attitudes towards the electoral process.
\end{list1}
{\bf Caucasus Research Resource Centers (CRRC), Eurasia Foundation},
Tbilisi, Georgia

\vspace{-.3cm}
{\em CRRC Deputy Director for Projects} \hfill {\bf
  September 2006--January 2010}\\

\vspace{-.3cm}
\begin{list1} 
\item[]-- Directed and helped implement CRRC assessments and evaluations,
  including supervision of USAID funded migration assessment in
  Armenia and a multiyear assessment of Millennium Challenge
  Corporation's (MCC) efficacy in economic development in
  Georgia. 
\item[]-- Coordinated CRRC Data Initiative (the largest cross-border
  survey in the Caucasus) and other survey and focus group activities,
  including questionnaire development, focus group guide development,
  questionnaire translation, expert meetings and report write-ups. 
\item[]-- Ran a 600,000 dollar election-related research program in
  cooperation with National Democratic Institute of International
  Affairs (NDI).
\end{list1}

\section{\sc Conference Presentations}
``Do Pre-Election Polls Changes Citizens' Beliefs or Behavior?
Evidence from a Laboratory Experiment in the Country of Georgia.''
Paper presented at Midwest Political Science Association Annual
Convention, Chicago, April 16-19, 2015.

``Power of the Panopticon? How Leaders' Images Affect Compliance.''
Paper presented at Midwest Political Science Association Annual
Convention, Chicago, April 16-19, 2015.

``Electoral Management Bodies in New Democracies:
Design, Transition and Legitimacy'' (with Nicholas Kerr). Paper
presented at 2014 IPSA World Congress of Political Science, Montreal, July 19-24, 2014. 

``Competing for Transparency: Political Competition and Administrative
Reform in Mexican States'' (with Daniel Berliner). Paper presented at
the 2013 APSA Annual Meeting, Chicago, August 29-September, 2013.

``Electoral Management Bodies and the Quality of Elections in
 sub-Saharan Africa between 1990 and 2010'' (with Stephan Hamberg).
Paper presented at
the 2013 APSA Annual Meeting, Chicago, August 29-September, 2013.

 ``The Political Determinants of Working Hour Regulation and Enforcement'' (with Magaret Levi and Jennifer Noveck). Paper presented at 2012 Society for the Advancement of
Socioeconomics (SASE) Conference, MIT, June 28-30, 2012.

``Who's Paying Attention to What? Armenian
 and Azerbaijani Perceptions of Conflict''  (with Arpine Porsughyan). Paper presented at 2009
 Association for the Study of Nationalities (ASN) Conference, Columbia
 University, New York, April 2009.

``Into Thin Air: Collecting Migration Statistics in the South
Caucasus.'' Paper presented at annual Central Eurasian Studies
Society Conference, University of Washington, Seattle, October 16--19, 2007.

\section{\sc Skills} 
\textbf{Statistical Packages}:  Stata, SPSS. \par\smallskip
\textbf{Computer Languages:} R, Python, bash and Unix shell scripts. \par\smallskip
\textbf{Computer Applications:} emacs, qGIS, ArcGIS, CSPro,  \LaTeX, Inquisit Millisecond.\par\smallskip
\textbf{Languages:} Proficient in Spanish; Research skills in
  Georgian, German, Russian; Rusty in Slovak; Elementary Turkish, Swahili.

\section{\sc Memberships}
American Political Science Association \\
Midwest Political Science Association

\section{\sc Field Research}
Armenia, 2006-2010  \\
Azerbaijan, 2006-2010\\
Georgia, 2006-2010, 2014-15 \\
Kenya 2010-2015 \\
South Africa, 2014 \\
Ukraine, 2014, 2015 \\
United Arab Emirates, 2015 \\

\section{\sc Service}
\textbf{Journal Reviewer: }\\
\emph{European Political Science Review}, \emph{Journal of International Relations and
  Development}, \emph{Journal of Politics} \par\smallskip
\textbf{Invited discussant}: \\
  Cambridge University Press Book Seminar on
Isabel Mares' manuscript \emph{From Open Secrets to Secret Voting}. Seattle, WA. Autumn 2014. \par\smallskip
 Severyns Ravenholt Comparative Politics Seminar on
Jesse Driscoll's' manuscript \emph{Warlords \& Coalition Politics in
  Post-Soviet States}. Seattle, WA. Autumn 2013. \par\smallskip
\textbf{Volunteer}: \\
Software Carpentry, 2013--  \\
Teach computational skills to
scientists.\par\smallskip
Transparify, 2013--\\
 Perform statistical analysis for NGO that promotes
financial transparency amongst NGOs.  \par\smallskip
\textbf{Graduate Student Member, Faculty Search Committee}, Big data
hire, 2013. \par\smallskip
\textbf{\LaTeX Trainer}, Teach introductory \latex course at the University of
Washington, 2010--. \par\smallskip
\textbf{Junior Faculty Development Program Interviewer} --- American Council for
International Education (ACCELS), 2007--2010. \par\smallskip
\textbf{International Election Observer}, South African 2014 General
Elections, Georgian 2008 Presidential Elections, 2008 Ach'aran Supreme
Council Elections. 

% % \clearpage
% \section{\sc References}
% %\scriptsize
% \begin{tabular}{lr}
% % Referee 1
% \begin{minipage}[t]{2.5in}
% \textbf{Margaret Levi}\\
% Director, Center for Advanced Study
% \\ in the Behavioral Sciences (CASBS),\\
% Professor of Political Science\\
% Stanford University \&\\
% Jere L. Bacharach Professor Emerita \\
% of International Studies, Political Science\\
% University of Washington \\
% \Telefon\ +1 (650) 736-0100\\
% \Letter \texttt{ \href{mailto:mlevi@stanford.edu}{mlevi@stanford.edu}}
% \end{minipage}
% &
% % Referee 2
% \begin{minipage}[t]{2.5in}
% \textbf{Christopher Adolph}\\
% Associate Professor of Political Science, \\
% Core Faculty of the Center for \\
% Statistics and Social Sciences,\\
% Adjunct Associate Professor of Statistics \\
% University of Washington\\
% \Telefon\ +1 (206) 543-2780 \\
% \Letter\ \texttt{\href{cadolph@uw.edu}{cadolph@uw.edu}}
% \end{minipage}
% \\
% \\ % Additional newline for spacing.
% % Referee 3
% \begin{minipage}[t]{2.5in}
% \textbf{Victor Menaldo}\\
% Associate Professor of Political Science\\
% University of Washington\\
% \Telefon\ +1(650) 814-9793\\
% \Letter\ \texttt{\href{vmenaldo@u.washington.edu}{vmenaldo@u.washington.edu}}
% \end{minipage}
% &
% % Referee 4
% \begin{minipage}[t]{2.5in}
% \textbf{James D. Long}\\
% Assistant Professor of Political Science\\
% University of Washington\\
% \Telefon\ +1 (206) 221-0396\\
% \Letter\ \texttt{\href{jdlong@uw.edu}{jdlong@uw.edu}}
% \end{minipage}
\\
% \\ % Additional newline for spacing.
% % Referee 3
% \begin{minipage}[t]{2.5in}
% \textbf{Mary O'Hagan}\\
% Country Director, Ukraine\\
% National Democratic Insitute (NDI)\\
% \Letter\ \texttt{\href{ohaganm@ndi.org }{ohaganm@ndi.org }}
% \end{minipage}
% &
% % Referee 4
% \begin{minipage}[t]{2.5in}
% \textbf{Hans Gutbrod, Ph.D. }\\
% Founder\\
% Transparify\\
% \Letter\ \texttt{\href{hans@transparify.org}{hans@transparify.org}}
% \end{minipage}
% \end{tabular}

\end{resume}
 \end{document}



